Maximum Entropy Spectral Analysis: a case study

### 2021-03-23 paper/mesa.tex
Added forecasting in temperatures

\sschmidt{Other comments below...}

@@

>>>>

We now assess the accuracy of the forecasting of new observations of the time series.
Based on actual data, we try to predict future values as described in sec.~\ref{sec:forecasting}. We produce $N =100$ indepedent predictions and we compute the median as well as the $90\%$ confidence interval. This is compared with the actual measured temparature values.
The predictions spans a two years range of time.
We report our results in fig.~\ref{fig:temp_spectrum}.

We note the observed difference is always well included in the $90\%$ confidence interval: the forecasting predictions seem reliable.
On the other hand, the confidence interval is pretty large (almost as large as $\SI{15}{K}$), thus making easy for the actual data to fit the predictions. We believe that the origin of such large uncertainty is due to the complexity of the time series considered: any realistic model, even more complex than our autoregressive process, might not produce drastically lower uncertainties (in such a long term).

\sschmidt{Data should be divided in train and test set for the purpose of forecasting!!}

\sschmidt{Other comments below??}

@@

\begin{figure}
	\caption{Difference between the historical temperature $T$ and the forecast temperature $T_{forecast}$ for two years of data. The red shadow denotes the $90\%$ confidence interval of the predictions. The model is trained with CAT loss function. The discrepancy between predicted and actual values is always everywhere included in the $90\%$ confidence interval.}
	\label{fig:temp_forecast}
	\includegraphics{Images/climate_plots/forecast_accuracy.pdf}
\end{figure}
